%-------------------------
% Resume in Latex
% Author : Alex Strand
% License : MIT
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    \textbf{#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}


\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://alexstrand.me}{\Large Alex Strand}} & Email : \href{mailto:ajstrand8@gmail.com}{ajstrand8@gmail.com}\\
  \href{http://alexstrand.me}{http://alexstrand.me} & Cell : 419-908-6212 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Olivet Nazarene University}{Bourbonnais, IL}
      {BA in Computer Science }{September 2011 - May 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  
     \resumeSubheading
      {OCLC}{Dublin, OH}
      {Software Engineer -  Identity Management Team}{Sept. 2018 - Present}
      \resumeItemListStart
\resumeItem 
{Working to convert Spring based applications to Spring Boot for a more consistent project structure for all of our applications. }
\resumeItem 
{Working with our UI/UX  team to implement a new Material Design interface for a login flow for one of our applications. This Material Design refactor will also reach other applications that my team controls providing a modern UI/UX to end users.}
        \resumeItem
<<<<<<< HEAD
          {Working with team members to move an application to ES6/TypeScript and adopt modern frontend tooling and processes. }
=======
          {Initiated/started efforts to move my team towards modern frontend tooling and practices, due to my prior work experience with front end technologies. }
          
          \resumeItem
          {Converting the front end of our user login application with team mates to ES6/TypeScript with team mates in an effort to modernize our front end code and create an organized approach to front end development for our team. }
>>>>>>> master
          
           \resumeItem
          {Eliminating dependencies on JQuery and YUI.js  allows us to ship much less code to an end user(from 30-40kb to just under 8kb). This provides a better user experience for end users using mobile devices in spotty network conditions. }
      \resumeItemListEnd

    \resumeSubheading
      {Root Inc.}{Sylvania, OH}
      {Software Developer}{Sept. 2015 - Sept. 2018}
      \resumeItemListStart
\resumeItem 
{Lead the rewriting of custom grunt plugins to work with a webpack build system for our SPA framework.  Utilizing webpack allowed us be consistent with the rest of our team's tech stacks for various projects}
\resumeItem 
{Lead the development to rebuild our jQuery SPA framework in ES6/Webpack instead of jQuery/Grunt. }
        \resumeItem
          {Worked with a team(also solo) to develop SPA apps for clients.}
        \resumeItem
          {Worked with  a team of developers to updates and add features to internal Node JS applications for our development team}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}

  \resumeSubHeadingListStart
  
  \resumeSubItem {ITF Taekwondo App}
{A reference app for android that lists all of the patterns in ITF Taekwondo for easy lookup.  }

  \resumeSubItem {Wikipedia Summaries}
{React/Go app that gives you the Wikipedia summary for topics or words that you enter.  Uses the Wikimedia REST API.}

\resumeSubItem{Daily Programmer Challange App}
{A React/Express web app that pulls a random challenge from r/dailyprogrammer on Reddit}
{Utilizes a javascript wrapper for Reddit's API(snoowrap). }


\resumeSubItem {Personal Site/blog}
 {A personal site and blog with a static generator that I developed written in Rust}


  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Languages and Technologies}
 \resumeSubHeadingListStart
 \item{
 \textbf{Languages}{: Javascript, HTML, CSS, Java}
 \hfill
\textbf{Technologies}{: React, Webpack, Jquery, Postgres SQL}
\textbf{Operating systems}{: Windows, MacOS, Linux}
}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}